New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-07-26 paper/answer_rev_1.tex
wip

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
%\newdefinition{rmk}{Remark}
%\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}

@@

		%\title{Cover Letter}
		%\maketitle

@@

			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.

		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.

		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.

>>>>

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
%\newdefinition{rmk}{Remark}
%\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}
\usepackage[dvipsnames]{xcolor}

@@

		%\title{Answer to Reviewer #1}
		%\maketitle

@@

		\opening{Answer to Reviewer \#1}
		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.

		The changes we have made to the text are highlighted by different colors. 
		\begin{itemize}
			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper derived.

			\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.

			\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.
		\end{itemize}

		Following we provide answers to each one of your comments:

		\textbf{Comment \#1:} ``(...) In particular, addressing under which real-world conditions the elliptical shape is the ideal shape to model coverage (...)".

		We address this issued by re-writing a piece of our introduction. The changes are in the ``Introduction" section (page 3). We decided to make a brief comment about the real-world applications of the problem and cite another work that explores this with greater detail. Also, because of the changes made to fit this comment, we ended up rewriting the next paragraph.

		\textbf{Comment \#2:} ``(...) Given fixed coverage areas, is it possible to allow minor and major axes to be decision variables to determine with shapes cover a particular space better? The aspect ratio and how elongated or circular the ellipses are at the final solution given different space densities might be an interesting issue to explore, rather than fixing the shape of the ellipses from the onset."

		We thought about this extension for a while, but it does not seem to be trivial to adapt the current method to make it work for this version of the problem, at least we could not figure out a way to do it. Also, we did not find any evidence that this particular extension has a real-world motivation behind it, so we decided not to further explore it in the main text, and just added a paragraph to the ``Conclusion" section (page 29) elaborating on some possible extensions (including this one) that could be the theme of future research.

### 2020-07-26 paper/answer_rev_2.tex
wip

		\opening{Answer to Reviewer \#1}
		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

@@

		The changes we have made to the text are highlighted by different colors. 
		\begin{itemize}
			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper derived.

			\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.

			\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.
		\end{itemize}

@@

		\textbf{Comment \#1:} ``(...) In particular, addressing under which real-world conditions the elliptical shape is the ideal shape to model coverage (...)".

		We address this issued by re-writing a piece of our introduction. The changes are in the ``Introduction" section (page 3). We decided to make a brief comment about the real-world applications of the problem and cite another work that explores this with greater detail. Also, because of the changes made to fit this comment, we ended up rewriting the next paragraph.

		\textbf{Comment \#2:} ``(...) Given fixed coverage areas, is it possible to allow minor and major axes to be decision variables to determine with shapes cover a particular space better? The aspect ratio and how elongated or circular the ellipses are at the final solution given different space densities might be an interesting issue to explore, rather than fixing the shape of the ellipses from the onset."

		We thought about this extension for a while, but it does not seem to be trivial to adapt the current method to make it work for this version of the problem, at least we could not figure out a way to do it. Also, we did not find any evidence that this particular extension has a real-world motivation behind it, so we decided not to further explore it in the main text, and just added a paragraph to the ``Conclusion" section (page 29) elaborating on some possible extensions (including this one) that could be the theme of future research.

>>>>

		\opening{Answer to Reviewer \#2}
		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

@@

		The changes we have made to the text are highlighted by different colors. 
		\begin{itemize}
			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper originated.

			\item The {\color{Red} red} highlights are corrections concerning the points made by reviewer \#1.

			\item The {\color{Green} green} highlights are corrections concerning the points made by reviewer \#2.

			\item The {\color{Orange} orange} highlights are corrections concerning points made by both reviewers.
		\end{itemize}

@@

		\textbf{Comment \#1:} `` The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."

		We address this issued by adding a paragraph to the end of our introduction, please see page 3 and 4.

		\textbf{Comment \#2:} ``In my opinion "fixed shape" ellipses should be replaced by "fixed shape parameters" ellipses, or ellipses with the given semi-major and semi-minor axes. Alternately the term "fixed shape" ellipses should be explained."

		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote some pieces of text were this was being used:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

			\item In the ``Introduction" section (page 3), we changed the description of our problem to: ``(...) each ellipse is defined to have fixed major and minor axis and an undefined location (...)."

			\item Section 4 had in its title (page 7) ``(...) of An Ellipse Given Its Shape and (...)", we replaced it by ``(...) of An Ellipse Given Its Shape Parameters and (...)."
		\end{itemize}

		\textbf{Comment \#3:} ``Please, extend the description of practical applications."
		We address this issued by re-writing a piece of our introduction. The changes are in the ``Introduction" section (page 3). We decided to make a brief comment about the real-world applications of the problem and cite another work that explores this with greater detail. Also, because of the changes made to fit this comment, we ended up rewriting the next paragraph.

		\textbf{Comment \#4:} ``The literature review in Introduction is a bit limited and should to be extended analyzing more approaches and references on the subject. It can be expected that beginning from the first publication [8] in 1984 a reasonable number of references on the subject have been published. See, e.g. papers: (...)"

		This issued is addressed in the ``Introduction" section on page 2. We agree with you that the literature review needed improvement, this is the sum-up of the changes we made:

		\begin{itemize}
			\item We add a citation to ``H Younies and G O Wesolowsky. Planar maximal covering location problem under block norm distance measure". This shows another example of versions of PMCLP other than the classical one using Euclidean norm.
			\item We add a citation to the survey paper: ``Alan T. Murray. Maximal coverage location problem: Impacts, significance, and evolution.". Instead of giving an extensive review, we use a common practice of citing a survey paper. 
		\end{itemize}

		Also, regarding the possible works that we could cite in our paper suggested by you, besides the PHD thesis of Daoqin Tong, who has some of his works cited in the above survey, we think that the other suggested papers seem not to be that closely related to our problem.

		\textbf{Comment \#5:} ``Please, clarify what is the critical parameter for your algorithm: the number of ellipses or the number of demand points?"

		We addressed this issue in section 8.2 ``New instances" (page 19). Now, we hope it is clear that the critical parameter is the number of ellipses.

		\textbf{Comment \#6:} ``In the paper overlapping of covering ellipses is allowed, i.e. a demand point can be covered by more than one ellipse. However, it seems natural that the weight of the demand point covered by various ellipses can differ from the weight of the same point covered by only one ellipse."

		We are using the same definition of PMCLP used in the several works we cited, maybe you could elaborate more why this seems natural?

		\textbf{Comment \#7:} ``What happens if no overlapping between covering ellipses is allowed. Please, comment on this."

		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.
		\href{http://www.sharelatex.com}{Something Linky}

### 2020-07-26 paper/article.tex
wip

\section{Determining Every Center and Angle of Rotation of An Ellipse Given Its Shape and Three Points that It Must Contain}\label{section:e3p}

>>>>

\section{Determining Every Center and Angle of Rotation of An Ellipse Given {\color{Red} Its Shape Parameters} and Three Points that It Must Contain}\label{section:e3p}

### 2020-07-26 paper/conclusion.tex
wip

{\color{Green}
	Finally, we leave some additional suggestions for future works on this subject. We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though, extensive work would be necessary to adapt, somehow, the theory developed for this version, especially, of MCER.
We also believe that investigating coverage of points by ellipsoids in higher dimensions can be a great subject of future studies taking this work as the starting point; 
coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective.
}

>>>>

{\color{Green}
	Finally, we leave some additional suggestions for future works on this subject. We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though extensive work would be necessary to adapt, somehow, the theory developed for this version, especially of MCER.
We also believe that investigating coverage of points by ellipsoids in higher dimensions can be a great subject of future studies taking this work as the starting point; 
coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective. 
%{\color{Red}
%	The last suggestion we give is that 
%	Lastly, as it has been pointed out, the critical parameter of both algorithms developed in this paper is the number of ellipses. We think that trading-off being able to run with large demand sets can be the basis for future work on an alternative algorithm that can obtain optimal solutions for instances with larger sets of ellipses.}
%}

### 2020-07-26 paper/introduction.tex
wip

%New paragraph
{\color{Green}
	In the real world, this problem comes up when a telecommunications company has to buy and place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming profit maximization. 
	More details about the applications of PMCLP can be found in \cite{canbolat}, which also ponders about the practical importance of considering the PMCLP with elliptical coverage.

@@

{\color{Red}
This paper is organized as follows. Section~\ref{section:definition} presents the definitions of both problems as well as introduces some notations used throughout the rest of the work. The algorithm for MCE is developed in Section~\ref{section:mce}, and the algorithm for MCER in Section~\ref{section:mcer} with the observation that its development depends on a subproblem whose algorithm is developed in Section~\ref{section:e3p}. Improvements suggestions to the implementations are given in Section~\ref{section:improvements} while the implementation details are given in Section~\ref{section:implementation}. Numerical results are presented and analyzed in Section~\ref{section:numerical}. Finally, a conclusion is given in Section~\ref{section:conclusion}.
}

>>>>

%New paragraph
{\color{Orange}
	In the real world, this problem comes up when a telecommunications company has to buy and place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming profit maximization. 
	More details about the applications of PMCLP can be found in \cite{canbolat}, which also ponders about the practical importance of considering the PMCLP with elliptical coverage.

@@

{\color{Red}
This paper is organized as follows. Section~\ref{section:definition} presents the definitions of both problems and introduces some notations used throughout the rest of the work. An algorithm for MCE is developed in Section~\ref{section:mce}, and an algorithm for MCER in Section~\ref{section:mcer} with the observation that its development depends on a subproblem whose algorithm is developed in Section~\ref{section:e3p}. Improvements suggestions to the implementations are given in Section~\ref{section:improvements} while the implementation details are given in Section~\ref{section:implementation}. Numerical results are presented and analyzed in Section~\ref{section:numerical}. Finally, a conclusion is given in Section~\ref{section:conclusion}.
}
